---
title: "name_list"
author: "Nick_Fox"
date: "4/30/2017"
output: html_document
---

Here I will generate the names to use in the social network questionnaires.

```{r echo = FALSE, message = FALSE}

#load packages
library(dplyr)
library(ggplot2)
library(tidyr)
library(tidytext)
library(RColorBrewer)

#set working directory
setwd("~/Dropbox/GitHub_master/data/PSYCHOLOGY_SOCIAL_NETWORKS")

fte_theme <- function() {
      
      # Generate the colors for the chart procedurally with RColorBrewer
      palette <- brewer.pal("Greys", n=9)
      color.background = palette[2]
      color.grid.major = palette[3]
      color.axis.text = palette[7]
      color.axis.title = palette[7]
      color.title = palette[8]
      
      # Begin construction of chart
      theme_bw(base_size=9) +
        
      # Set the entire chart region to a light gray color
      theme(panel.background=element_rect(fill=color.background, color=color.background)) +
      theme(plot.background=element_rect(fill=color.background, color=color.background)) +
      theme(panel.border=element_rect(color=color.background)) +
      
      # Format the grid
      theme(panel.grid.major=element_line(color=color.grid.major,size=.25)) +
      theme(panel.grid.minor=element_blank()) +
      theme(axis.ticks=element_blank()) +
      
      # Format the legend, but hide by default
      #theme(legend.position="none") +
      theme(legend.background = element_rect(fill=color.background)) +
      theme(legend.text = element_text(size=10,color=color.axis.title)) +
      
      # Set title and axis labels, and format these and tick marks
      theme(plot.title=element_text(color=color.title, size=16, vjust=1.25)) +
      theme(axis.text.x=element_text(size=10,color=color.axis.text)) +
      theme(axis.text.y=element_text(size=10,color=color.axis.text)) +
      theme(axis.title.x=element_text(size=12,color=color.axis.title, vjust=0.5)) +
      theme(axis.title.y=element_text(size=12,color=color.axis.title, vjust=0.5)) +
      
      # Plot margins
      theme(plot.margin = unit(c(0.35, 0.2, 0.3, 0.35), "cm"))
    }

#ggplot themes for figures to look a little more like 538 blog figures
```


```{r echo = FALSE}

#read in the csv file
all_names <- read.csv("name_list.csv", header = TRUE)

#create df with all present names (no absent)
present_email <- all_names %>% 
  filter(status_2017 != "absent") %>%
  filter(status_2017 != "Absent") %>% 
  filter(email != "")

#filter to only keep entries that have a first name
present_email_firstnames <- present_email %>% 
  filter(first_name != "")


```

How the list has changed since 2010:
```{r echo = FALSE}

#look at how the list has changed since being first collected in 2010
all_names %>% 
  group_by(status_2017) %>% 
  count(status_2017)

```

2281 researchers no longer listed on their departmental website. <br>
3097 new researchers on departmental websites. <br>
874 changed/updated email addresses. <br>
----------------------
<br>
----------------------

Choosing names - Based on previous research, want to choose names that account for ~ 0.1%-0.2% of the population.

```{r echo = FALSE}
#generate frequency for last names in the population
present_lastname_freq <- present_email_firstnames %>% 
  group_by(last_name) %>% 
  summarise(n = n()) %>% 
  mutate(freq_lastname = n / sum(n))

#generate the list of names to use for "total known population"
#previous literature suggests using names that represent 0.1%-0.2% of the population
total_population_names <- present_lastname_freq %>% 
  filter(freq_lastname < 0.002) %>% 
  filter(freq_lastname > 0.00095) %>% 
  arrange(desc(freq_lastname))

print(total_population_names)

total_population_names %>% 
  ggplot(aes(x = reorder(last_name, freq_lastname), y = freq_lastname, fill = last_name)) + geom_bar(stat = "identity") + coord_cartesian(ylim = c(0.0005, 0.003)) + fte_theme() + labs(title="Last Names Accounting for 0.095% - 0.2%\nof All Psychologists", x="\nLast Name", y="Population Proportion\n") + geom_hline(yintercept=0.3, size=0.4, color="black") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + guides(fill=FALSE)


```

----------------------
----------------------
<br>

Next I want to compile Common, Uncommon, and Rare first names for the Game of Contacts

```{r echo = FALSE}

present_email_firstnames$first_name <- gsub(' [A-z ]*', '' , present_email_firstnames$first_name)


present_firstname_freq <- present_email_firstnames %>% 
  group_by(first_name) %>% 
  summarise(n = n()) %>% 
  mutate(freq_firstname = n / sum(n)) %>% 
  arrange(desc(n))

print(present_firstname_freq)

```

By roughly cutting the total list into thirds, I've generated categories that include roughly equal numbers of people.  They are unequal due to including all of the names at appear a certain amount of times (i.e, 5 people with the same name) in the same category.  If having 5 people with the same name is considered "common", then every name with 5 people should be in that category, not arbitrarily cut off between "common" and "uncommon"

```{r echo = FALSE}
#catogorize first names names as common/uncommon/rare 

#generate the cumuluative frequency of names
name_cat <- present_firstname_freq %>% 
  mutate(cum_freq = cumsum(n))

#roughly based on 1/3s, make cutoffs based on frequency of name
name_cat <- name_cat %>% 
  mutate(category = cut(n, breaks = c(0, 4, 23, Inf), labels = c("rare", "uncommon", "common")))

#summarise how many total people are in each category
name_cat %>%
  group_by(category) %>% 
  summarise(cat = sum(n))

```

For the Game of Contacts, I will need to select 24 names: <br>
8 Common <br>
8 Uncommon <br>
8 Rare <br>

From these, each should have 4 male names and 4 female names. <br>

((will I have to enter the gender data for all names??))

-----

5/3/17

-I think I need to go back and review the phone book method for the general population.

-I have first names that I can use for Popularity Ratio and Game of Contacts (based on commonality)

NEXT STEPS) Nail down the phone book method for general population and start making the questionnaire.

